Draft information

### 2019-06-07 paper/draft-info.Rmd
Updates to draft info

---
title: "Draft information"
subtitle: "version: draft-6.1"
date: "2019-05-23"
# author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
bibliography: bibliography.bib
csl: plos-biology.csl
output:
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
# classoption: twocolumn
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[M-]{manuscript}

---

@@

@@

* Moved figures at the end of the manuscript
* Refer to Figures as "Fig." in the main text
* Minor correction to Figure 2 caption

>>>>

---
title: "Draft information"
subtitle: "version: draft-7.0"
date: "2019-06-07"
# author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
# bibliography: bibliography.bib
# csl: plos-biology.csl
output:
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
# classoption: twocolumn
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[M-]{manuscript}
---

@@

## Requests to coauthors

* Check text between \lr{M-start-deposition-facil-competition} and \lr{M-end-deposition-facil-competition} where there were changes.
* Check the cover letter. I made small changes based on assessment from EL editor and swapped the order of a couple paragraphs. 
* __Jason__: Could you please double check your grant numbers? They look different to Daniel's.

@@

* Renamed visit effectiveness as visit potential throughout to reduce confusion with previous uses of the term.
* Corrected a mistake on the names used for the model terms in Table S5. It used to say "degree" where it should have been "# shared pollinators".
* Corrected caption of Fig S3 which used "trait originality" instead of "functional originality" which is the term we use in the paper
* Paper has been formatted with minimum requirements for initial submission at Plos Biology.
* Added some sentences in the intro to strengthten the link between competition/facilitation and conspecific/heterospecific pollen.
